A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-06-08 report_clean_merged/intro.tex
added report merged with the files of Lise-Marie and Bruno

\urev{
We consider the wave propagation in the cold plasma that consists of particles of single species 
under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. In two dimensions, in the plane 
perpendicular to the direction of the magnetic field, this process can be described by the time-dependent Maxwell system  \cite{Stix}
\begin{align}
\label{eq:main_system}
\begin{split}
-\epsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
-\epsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
\mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
\end{split}
\end{align}
coupled with the equations for the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$
\begin{align}
\begin{split}
\label{eq:electronmove}
m_e \partial_t u_x =\epsilon_0 e E_x+e B_0(\mathbf{r}) u_y -m_e \nu u_x,\\
m_e \partial_t u_y =\epsilon_0 e E_y-e B_0(\mathbf{r}) u_x -m_e \nu u_y,
\end{split}
\end{align}
where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density that in general 
depends on spatial variables and is uniform in time. A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle. 
The unknowns are the electron velocity $\ubf$ and the electromagnetic field.

The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014},
\ben
{\mathcal E}(t)= \int_\Omega \left(
\frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\mathbf{r})|^2}{2|e|N_e(\mathbf{r})} 
\right)\mathrm{d}\mathbf{r},
\een
and
\ben
\frac{d}{dt}{\mathcal E}=-\nu\left(\|u_{x}\|_{L^{2}(\Omega)}^2+\|u_{y}\|_{L^{2}(\Omega)}^2\right)+\text{boundary terms}.
\een

To illustrate unexpected difficulties that can occur in this system, let us rewrite it in the frequency domain. To do so, 
we introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
in time of (\ref{eq:main_system}) (with the convention $\partial_t\rightarrow -i\omega$), for a 
particular case $\nu=0$:
\begin{align}
\label{eq:model_freq_domain}
 \mathbf{curl}{\operatorname{curl}}\hat{\mathbf{E}}-\frac{\omega^2}{c^2}\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})\hat{\mathbf{E}}=0,
\end{align}
where the cold-plasma dielectric tensor \cite[Chapter 1-2]{Stix}
\begin{align}
\nonumber
\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})=\left(
 \begin{matrix}
  \alpha_{\omega}(\mathbf{r})& -i\delta_{\omega}(\mathbf{r})\\
  i\delta_{\omega}(\mathbf{r}) & \alpha_{\omega}(\mathbf{r})
 \end{matrix}
\right),\\
\label{eq:alpha_delta}
\alpha_{\omega}(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta_{\omega}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
\end{align}

@@

Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$ and $\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})\neq 0$, i.e. when the diagonal part of the tensor 
$\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case.

As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
integrable (for a demonstration of this behaviour with the help of a simpler example, namely the Budden problem, see e.g. \cite{Despres_2014}). 
This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.

Before proceeding, let us define the geometrical setting of the problem. We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in the domain $(-L,\;\infty)\times\mathbb{R},\; L>0$, with the 
 boundary conditions chosen as follows. At the left boundary of the domain, which represents the wall of the Tokamak, we pose Robin boundary conditions 
\be
\label{eq:boundary_conditions_intro}
curl \hat{\mathbf{E}} \mrev{+}i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} \mrev{+}\imath\lambda\E_{inc}\wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
the frequency of the antenna. We truncate the domain 
$(-L,\; \infty)\times\mathbb{R}$ to $(-L,\; H)\times\mathbb{R},\; H>0,$ and set on the right boundary $\operatorname{curl} \hat{\E} = 0$.

In this article we concentrate on a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas), 
where it is required to study the above system under the assumption that the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate, more precisely 
$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. 
We additionally assume that $N_e>0$ on $[-L,\;H]$. Even this simplified case contains difficulties intrinsic to the hybrid resonance \cite{Despres_2014, singular_solutions}.

Under the aforementioned assumptions on $N_e$ and $B_0$, the one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$):
\begin{equation}
 \label{eq:main_model}
\begin{cases}
\epsilon_0\partial_t E_{x}-i\theta H_z=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
\mu_0\partial_t H_z+\partial_x E_y-i\theta E_x =0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y,
\end{cases}
\end{equation}
 posed in $(-L,\; H)$, for some $L,H>0$, with \mrev{the boundary conditions as in (\ref{eq:boundary_conditions_intro})
 \begin{align}
 \label{eq:boundary_conditions_frequency_domain}
 \begin{split}
  \left.\left(\partial_x E_y -i\theta E_x+i\lambda E_y\right)\right|_{x=-L} =g_{inc}(t),\\
  \left.\partial_xE_y\right|_{x=H}=0, 
  \end{split}
 \end{align}
and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. }

This is the time-domain model that will be considered in the rest of the article, unless stated otherwise.

In the frequency domain (\ref{eq:main_model}) for $\nu=0$ is of the form 
\begin{align}
\label{eq:main_frequency_domain_intro}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\uuline{\varepsilon_{\omega}^{0}}(x)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
see (\ref{eq:alpha_delta}). Indeed, the coefficients $\alpha_{\omega},\;\delta_{\omega}$, see (\ref{eq:alpha_delta}), in this case depend solely on $x$ and $\omega$.  
\arev{
We concentrate on a physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
\begin{df}
Let $\omega\in\mathbb{R}$ be fixed. 
We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of this point $B_{\epsilon}(x_h)$, for some $\epsilon>0$, 
and $\delta_{\omega}(x_h)\neq 0$.
\end{df}
}

To investigate the behaviour of the solutions in the case when the hybrid resonance occurs in the system, 
instead of the above problem we will study a sequence of the regularized problems, for $\nu\rightarrow 0$, 
\begin{align}
\label{eq:seq_regularized}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
where $\mathrm{Id}$ is the identity matrix. More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.

@@

The goal of this article is three-fold. 
First, we investigate the finite element approximation of the 1D 
problem (\ref{eq:seq_regularized}), with a dielectric tensor \mrev{regularized
with the help of a small parameter $\nu$}. 
%linearized with respect to $\nu$.
We prove the well-posedness of this problem for \mrev{$\nu\neq 0$} in Section~\ref{sec:wellposedness} and 
demonstrate that the use of  $P_1$ finite elements allows to approximate the singularity 
of the solution fairly well (Section \ref{sec:freq_dep}). 
}

Second, we briefly develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Thirdly, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which is equivalent to considering
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) 
would approach the solution of (\ref{eq:main_frequency_domain_intro})
as $\nu\rightarrow 0$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$ and the boundary condition $\left.\partial_x \hat{E}_y\right|_{x=-L}=1$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then writes as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in our case due to the singularity
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);

>>>>

\urev{
We consider the time-dependent wave propagation problem leading to the cold plasma model for a single species 
under a uniform in time background magnetic field $\mathbf{B}_0=(0,\;0,\; B_0)$. 
We restrict our attention to the poloidal plane, which is the plane 
perpendicular to the direction of the magnetic field. The model can be described by the time-dependent Maxwell system  \cite{Stix}
\begin{align}
\label{eq:main_system}
\begin{split}
-\epsilon_0 \partial_t E_x +\partial_y H_z = J_x,\\
-\epsilon_0 \partial_t E_y -\partial_x H_z = J_y,\\
\mu_0 \partial_t H_z + \partial_x E_y-\partial_y E_x= 0
\end{split}
\end{align}
coupled through the linear electronic current  $\J = eN_e(\mathbf{r}) \ubf$
 with the equations 
 \begin{align}
\begin{split}
\label{eq:electronmove}
m_e \partial_t u_x =\epsilon_0 e E_x+e B_0(\mathbf{r}) u_y -m_e \nu u_x,\\
m_e \partial_t u_y =\epsilon_0 e E_y-e B_0(\mathbf{r}) u_x -m_e \nu u_y,
\end{split}
\end{align}
where \mrev{$\nu\geq 0$} is the friction  between particles, $e<0$ is the charge of electrons, $m_e$ the electron mass and $N_e$ the electron density. In the cold plasma model, because of the frequencies considered, the electron density 
depends on space and is uniform in time. A non-zero value of $\nu$ constitutes a basis for the limiting absorption principle. 
The unknowns are the electron velocity $\ubf$ and the electromagnetic fields.

The energy of this system in a domain $\Omega\in\mathbb R^2$ can be expressed as, see \cite{Despres_2014},
\ben
{\mathcal E}(t)= \int_\Omega \left(
\frac{\epsilon_0 |\E(t,\mathbf{r})|^2}{2}+\frac{ |\B(t,\mathbf{r})|^2}{2\mu_0}+\frac{m_e|\J (t,\mathbf{r})|^2}{2|e|N_e(\mathbf{r})} 
\right)\mathrm{d}\mathbf{r},
\een
and (\ref{eq:main_system}-\ref{eq:electronmove}) yield to
\ben
\frac{d}{dt}{\mathcal E}=-\nu\left(\|u_{x}\|_{L^{2}(\Omega)}^2+\|u_{y}\|_{L^{2}(\Omega)}^2\right)+\text{boundary terms}.
\een

To illustrate unexpected difficulties that can occur in this system, consider the frequency domain counterpart of (\ref{eq:main_system}-\ref{eq:electronmove}), which corresponds to the cold plasma model. To do so, 
we introduce the plasma frequency $\omega_p(\mathbf{r})=\sqrt{\frac{|e|^2N_e(\mathbf{r})}{m\epsilon_0}}$, 
the cyclotron frequency $\omega_c(\mathbf{r})=\frac{e B_0(\mathbf{r})}{m_e}$ and perform the Fourier transform 
in time of (\ref{eq:main_system}-\ref{eq:electronmove}) (with the convention $\partial_t\rightarrow -i\omega$), for a 
particular case $\nu=0$:
\begin{align}
\label{eq:model_freq_domain}
 \mathbf{curl}\  {\operatorname{curl}}\  \hat{\mathbf{E}}-\frac{\omega^2}{c^2}\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})\hat{\mathbf{E}}=0,
\end{align}
where the cold-plasma dielectric tensor \cite[Chapter 1-2]{Stix}
\begin{align}
\nonumber
\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})=\left(
 \begin{matrix}
  \alpha_{\omega}(\mathbf{r})& -i\delta_{\omega}(\mathbf{r})\\
  i\delta_{\omega}(\mathbf{r}) & \alpha_{\omega}(\mathbf{r})
 \end{matrix}
\right),\\
\label{eq:alpha_delta}
\alpha_{\omega}(\mathbf{r})=1-\frac{\omega_p^2(\mathbf{r})}{\omega^2-\omega_c^2(\mathbf{r})},\; \delta_{\omega}(\mathbf{r})=\frac{\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})}{\omega(\omega^2-\omega_c^2(\mathbf{r}))}.
\end{align}

@@

Another interesting case is $\omega_p^2(\mathbf{r})+\omega_c^2(\mathbf{r})=\omega^2$ and $\omega_c(\mathbf{r})\omega_p^2(\mathbf{r})\neq 0$, i.e. when the diagonal part of the tensor 
$\uuline{\varepsilon_{\omega}^{0}}(\mathbf{r})$ vanishes and the non-diagonal part remains non-zero. This is a hybrid resonance case. 
As shown in \cite{Despres_2014, singular_solutions}, for a 1D-counterpart of (\ref{eq:model_freq_domain}), in this case the time-harmonic electric field component $E_x$ is not necessarily square 
integrable (for a demonstration of this behaviour with the help of a simpler example, namely the Budden problem, see e.g. \cite{Despres_2014}). 
This apparent paradox is of course the source of important numerical difficulties which are the subject of the present study.

Before proceeding, let us define the geometrical setting of the problem. 
We consider the frequency domain problem (\ref{eq:model_freq_domain}) posed in a truncated infinite half-plane, $(-L,\;H)\times\mathbb{R}$, for some $L>0$ and $H>0$, with the following
 boundary conditions. At the left boundary of the domain, which represents the wall of the Tokamak, we impose a Robin boundary condition
\be
\label{eq:boundary_conditions_intro}
curl \hat{\mathbf{E}} \mrev{+}i \lambda\hat{\mathbf{E}}\wedge \n = \hat{g}_{inc} =curl \E_{inc} \mrev{+}\imath\lambda\E_{inc}\wedge \n,
\ee
where $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$ and \mrev{$\lambda\geq 0$} is 
the frequency of the antenna. At the right boundary we impose $\operatorname{curl} \hat{\E} = 0$.

In this work we focus on stratified medium case: we suppose that
%a simplified model (which nevertheless is of physical interest when modelling antennas in plasmas),  where it is required to study the above system under the assumption that 
the electron density $N_{e}$ and the magnetic field $B_0$ are \textbf{uniform} in the second coordinate $y$,
$N_{e}=N_{e}(x)$ and $B_0=B_0(x)$, see e.g. \cite{Despres_2014}. 
We additionally assume that $N_e>0$ on $[-L,\;H]$. We choose this simplified case to focus on the fundamental mathematical difficulties of the hybrid resonance \cite{Despres_2014, singular_solutions}.

Under the aforementioned assumptions on $N_e$ and $B_0$, the one-dimensional model can be derived from (\ref{eq:main_system}) by performing the Fourier transform in $y$ ($\partial_y\rightarrow i\theta, \; \theta\in\mathbb{R}$):
\begin{equation}
 \label{eq:main_model}
\begin{cases}
\epsilon_0\partial_t E_{x}-i\theta H_z=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H_z=-eN_e u_y,\\
\mu_0\partial_t H_z+\partial_x E_y-i\theta E_x =0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y,
\end{cases}
\end{equation}
 posed in the one dimension domain $(-L,\; H)$, with \mrev{the corresponding boundary conditions:
 \begin{align}
 \label{eq:boundary_conditions_frequency_domain}
 \begin{split}
  \left.\left(\partial_x E_y -i\theta E_x+i\lambda E_y\right)\right|_{x=-L} =g_{inc}(t),\\
  \left.\partial_xE_y\right|_{x=H}=0, 
  \end{split}
 \end{align}
and the initial conditions for values $\left.E_{x}\right|_{t=0},\; \left.u_{x}\right|_{t=0},\; \left.E_{y}\right|_{t=0}, \; \left.u_{y}\right|_{t=0}, \; \left.H_z\right|_{t=0}$. }
This is the time-domain model that will be considered in the rest of the article, unless stated otherwise.

The frequency domain formulation of (\ref{eq:main_model}) for $\nu=0$ is
\begin{align}
\label{eq:main_frequency_domain_intro}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\uuline{\varepsilon_{\omega}^{0}}(x)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
see (\ref{eq:alpha_delta}). Indeed, in a stratified medium, the coefficients $\alpha_{\omega},\;\delta_{\omega}$ depend solely on $x$ and $\omega$.  
\arev{
We concentrate on a physical situation of the hybrid resonance, which we define as in \cite{singular_solutions}.
\begin{df}
Let $\omega\in\mathbb{R}$ be fixed. 
We will call a point $x_h\in \mathbb{R}$ a hybrid resonance if $\alpha_{\omega}$ has 
a simple root in $x_h$ and has no other roots in an $\epsilon$-vicinity of this point $B_{\epsilon}(x_h)$, for some $\epsilon>0$, 
and $\delta_{\omega}(x_h)\neq 0$.
\end{df}
}

To investigate the behaviour of the solutions at the hybrid resonance, 
we will study a sequence of the regularized problems, for $\nu\rightarrow 0$. These problems are not the frequency domain expression of \eqref{eq:main_model}, but a simple regularization of \eqref{eq:main_frequency_domain_intro}. This choice will be justified in further sections. The equations read: 
\begin{align}
\label{eq:seq_regularized}
\left(
\begin{matrix}
 i\theta \partial_x \hat{E}_y+\theta^2 \hat{E}_x\\
 i\theta \partial_x \hat{E}_x -\partial_x^2 \hat{E}_y
\end{matrix}
\right)-\frac{\omega^2}{c^2}
\left(\uuline{\varepsilon_{\omega}^{0}}(x)+i\nu \mathrm{Id}\right)\left(
\begin{matrix}
 \hat{E}_x\\
 \hat{E}_y
\end{matrix}
\right)
=0,
\end{align}
where $\mathrm{Id}$ is the identity matrix. %More details on the connection of this problem with (\ref{eq:main_model}) will be provided in further sections.

@@

The goal of this article is three-fold. 
First, we investigate the finite element approximation of the 1D 
frequency domain problem (\ref{eq:seq_regularized}), with a regularized dielectric tensor \mrev{for a small parameter $\nu$}. 
%linearized with respect to $\nu$.
We prove the well-posedness of this problem for \mrev{$\nu\neq 0$} in Section~\ref{sec:wellposedness} and 
demonstrate that the use of  $P_1$ finite elements allows to approximate the singularity 
of the solution efficiently (Section \ref{sec:freq_dep}). 
}
Second, we develop an original scheme based on widely appreciated semi-lagrangian schemes
for the discretization of time domain Maxwell's equations with a linear current.
Third, we consider the case $\nu\rightarrow 0$, and study the limiting amplitude solution 
$\lim\limits_{t\rightarrow +\infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}(t)$ obtained with the help of 
the FDTD discretization of \eqref{eq:main_model}, suggested in \cite{stable_yee_plasma_current}. 
We compare this result with 
$\hat{\mathbf{E}}\mathrm{e}^{\mrev{-i\omega} t}$, computed in the frequency domain, for $\nu\rightarrow 0$, which corresponds to
$\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}\mathbf{E}(t)$.
\urev{Such a comparison is a way to study the formal commutation relation between the limited absorption and the limiting amplitude principles. 
In application to a non-resonant case of (\ref{eq:main_frequency_domain_intro}), equipped with boundary conditions, the limited absorption principle states that the solution of (\ref{eq:seq_regularized}) 
would approach the solution of (\ref{eq:main_frequency_domain_intro})
as $\nu\rightarrow 0$. Similarly, the limiting amplitude principle applied to the problem (\ref{eq:main_model}) 
states that if the boundary conditions are chosen harmonic in time, e.g. $\left.\partial_x E_y\right|_{x=-L}=\mathrm{e}^{-i\omega_{*} t}$, then the solution of this problem $(\mathbf{E}(t),\;H(t))$ asymptotically ($t\rightarrow +\infty$)
tends to a steady state of the form $ \left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)\mathrm{e}^{-i\omega_{*} t}$, where 
$\left(\hat{\mathbf{E}}(\omega_{*}),\; \hat{H}(\omega_{*})\right)$ is the solution of (\ref{eq:main_model})
in the frequency domain, with $\omega=\omega_{*}$ and the boundary condition $\left.\partial_x \hat{E}_y\right|_{x=-L}=1$. For more details see e.g. \cite{Morawetz, Eidus}. The commutation between the two principles then writes as}
$$
\lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow+\infty}= \lim\limits_{t\rightarrow+\infty}\lim\limits_{\nu\rightarrow 0},
$$
see Figure \ref{fig:limits}. 
Even though it is true for standard linear wave problems, it is not clear \mrev{if it still holds} in the singular case 
of the hybrid resonance.
\begin{figure}
\begin{tikzpicture}
   \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em] {
     \mathbf{E}^{\nu}(t) & \mathbf{E}^{0+}(t)\\
     \hat{\mathbf{E}}^{\nu}(t)\mathrm{e}^{i\omega t} & 
    \lim\limits_{\nu\rightarrow 0}\lim\limits_{t\rightarrow \infty}\mathbf{E}^{\nu}(t)=\lim\limits_{t\rightarrow \infty}\lim\limits_{\nu\rightarrow 0}\mathbf{E}^{\nu}(t)\\
     };
 \path[-stealth,font=\scriptsize]    (m-1-1) edge node [left] {$t\rightarrow+\infty$} (m-2-1);
  \path[-stealth, font=\scriptsize]   (m-1-1) edge node [above] {$\nu\rightarrow 0+$} (m-1-2);
 \path[-stealth, font=\scriptsize]   (m-2-1) edge node [above] {$\nu\rightarrow 0$} (m-2-2);
  \path[-stealth, font=\scriptsize]   (m-1-2) edge node [right] {$t\rightarrow +\infty$} (m-2-2);
